Hydraulically-vulnerable trees survive on deep-water access during droughts in a tropical forest

### 2020-11-06 Supporting_Information.Rmd
Updated growth data description to match with the main text

## Data Descriptions 
### Growth Data 
\
We selected trees for which the height of the diameter measurements were unchanged across all censuses (1990, 1995, 2000, 2005, 2010, 2015). For each individual tree ($i$), we calculated absolute growth rates ($G_{i,t}$, cm yr^-1^) for each of the five census intervals ($t$) as the difference between tree dbh measured in successive censuses prorated by the inter-census interval based on the exact date of measurements. We eliminated positive outliers as any growth rates amounting to >75 mm yr^-1^, as this was the highest rate observed with confidence for the fastest growing species [@Condit.2017]. Negative outliers were removed based on known measurement error, $\sigma_{e} = 0.006214d + 0.903$, where *d* is dbh. Any stem whose later dbh measurement fell <4$\sigma_{e}$ the earlier measurement was removed [@Condit.2017]. As tree growth rates vary with size [@Muller-Landau:2006], to keep growth rates comparable across census intervals, we obtained residuals from a dbh model of tree growth based on a tree's dbh at the beginning of a census interval ($\textrm{Resid}_{i,t} = G_{i,t} - f(d_{i,t})$). The diameter model of growth, $f(d_{i, t})$, a B-spline based polynomial equation with five degrees of freedom, was fitted to growth rates from all trees pooled together as there was insufficient species-specific data for large trees ($R$^2 = 0.27; $p$-value < 0.01). We retained only those trees that had $\textrm{Resid}_{i,t}$ estimates for all census intervals (total trees = `r sum(g.n$n)`) and standardized (centered and scaled) individual tree time series of $\textrm{Resid}_{i,t}$. We then obtained `r length(erd.sp)` species-level time-series of medians of $\textrm{Resid}_{i,t}$ ($G_{t}$). These were obtained for only those species with complete records on at least three trees (median $n$ = `r median(g.n$n)`, max $n$ = `r max(g.n$n)` trees per species).

>>>>

## Data Descriptions 
### Growth Data 
\
We selected trees for which the height of the diameter measurements were unchanged across all censuses (1990, 1995, 2000, 2005, 2010, 2015). For each individual tree ($i$), we calculated absolute growth rates ($\grave{G}_{i,t}$, cm yr^-1^) for each of the five census intervals ($t$) as the difference between tree dbh measured in successive censuses prorated by the inter-census interval based on the exact date of measurements. We eliminated positive outliers as any growth rates amounting to >75 mm yr^-1^, as this was the highest rate observed with confidence for the fastest growing species [@Condit.2017]. Negative outliers were removed based on known measurement error, $\sigma_{e} = 0.006214d + 0.903$, where *d* is dbh. Any stem whose later dbh measurement fell <4$\sigma_{e}$ the earlier measurement was removed [@Condit.2017]. As tree growth rates vary with size [@Muller-Landau:2006], to keep growth rates comparable across census intervals, we obtained residuals $\textrm{R}_{i,t}$ from a dbh model of tree growth based on a tree's dbh at the beginning of a census interval ($\textrm{R}_{i,t} = \grave{G}_{i,t} - f(d_{i,t})$). The diameter model of growth, $f(d_{i, t})$, a B-spline based polynomial equation with five degrees of freedom, was fitted to growth rates from all trees pooled together as there was insufficient species-specific data for large trees ($R$^2 = 0.27; $p$-value < 0.01). We retained only those trees that had $\textrm{R}_{i,t}$ estimates for all census intervals (total trees = `r sum(g.n$n)`) and standardized (centered and scaled) individual tree time series of $\textrm{Resid}_{i,t}$. We then obtained growth time series $G_{s}$ for each species $s$ as the time-series of medians of $\textrm{R}_{i,t}$ for use in the ERD model. These were obtained for only those species ($n$ = `r length(erd.sp)`) with complete records on at least three trees (median $n$ = `r median(g.n$n)`, max $n$ = `r max(g.n$n)` trees per species).
